Effect of quality-adjusted production function inputs

### 2015-05-15 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Fixed capital services vs. stock bug.

<<Formulas>>=
# Set up the formulas for each type of analysis.
# These formulas contain energy. 
# We can use keep_summands to drop the energy term (3rd summand on the rhs)
# later if needed.
formulas <- 
  list( 
    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
    UK = c(unadjusted = build_formula("iGDP", list("iKservO.WwithRD", "iL", "iXp", "iYear")),
             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
  )
countries <- names(formulas)
@

@@

# Relevel factors before plotting
fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
fitted_and_resid_data$adjusted <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With Energy"))
@

@@

<<Fitted and Residual Graphs>>=
fittedGraph <- function(data){
  ggplot() +
    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
    scale_linetype_manual(values=c(2,3), name="") +
    facet_grid(Country ~ flavor) +
    xy_theme()
}

residualPlot <- function(data){
  ggplot() +
    geom_line(data=data, mapping=aes(x=Year, y=Residuals, linetype=energy)) +
    scale_linetype_manual(values=c(2,3), name="") +
    facet_grid(Country ~ flavor) +
    xy_theme()
}
@

@@

\begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
\label{tab:lambda_CES-lek_PT} 
  \begin{center}
    \begin{tabular}{r c c} 
      \toprule
                      & Unadjusted     & Quality-adjusted   \\
      \midrule
      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
                                        & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$lek)$lambda} 
                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CESle)$lambda} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

>>>>

<<Formulas>>=
# Set up the formulas for each type of analysis.
# These formulas contain energy. 
# We can use keep_summands to drop the energy term (3rd summand on the rhs)
# later if needed.
formulas <- 
  list( 
    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
  )
countries <- names(formulas)
@

@@

# Relevel factors before plotting
fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
fitted_and_resid_data$flavor <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With Energy"))
@

@@

<<Fitted and Residual Graphs>>=
fittedGraph <- function(data){
  ggplot() +
    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
    scale_linetype_manual(values=c(2,3), name="") +
    facet_grid(Country ~ flavor) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xy_theme()
}

residualPlot <- function(data){
  ggplot() +
    geom_line(data=data, mapping=aes(x=Year, y=Residuals, linetype=energy)) +
    scale_linetype_manual(values=c(2,3), name="") +
    facet_grid(Country ~ flavor) +
    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
    xy_theme()
}
@

@@

\begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
\label{tab:lambda_CES-lek_PT} 
  \begin{center}
    \begin{tabular}{r c c} 
      \toprule
                      & Unadjusted     & Quality-adjusted   \\
      \midrule
      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
                                        & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$lek)$lambda} 
                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CES$lek)$lambda} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}
